### 2015-05-13 whoop.tex
update

\medskip\noindent\textbf{Assumptions }
%
We assume that the formal parameters of an entry point do not alias, and thus cannot race. This is a potentially unsound feature that can be turned off using a command line option. In our experience so far, though, we have not missed any data races because of this assumption. We also assume that our environmental model and domain-specific knowledge are correct and do not cause any bugs to be missed. Finally, we assume that the external tools we use as part of the \whoop toolchain are sound and bug-free.

\medskip\noindent\textbf{Limitations }
%
\whoop is based on lockset analysis and thus can report false bugs, because a violation of the locking discipline does not always correspond to a real data race (e.g.\ when lockfree synchronization is used instead of locking). \whoop also uses over-approximation (e.g.\ when reading from the shared state) and summarization, which can be sources of false positives. Furthermore, the tool does not currently check for dynamically created locks or for locks that are provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks.

\PDComment{briefly mention interrupts}

>>>>

\medskip\noindent\textbf{Assumptions }
%
We assume that the formal parameters of an entry point do not alias, and thus cannot race. This is a potentially unsound feature that can be turned off using a command line option. In our experience so far, though, we have not missed any races because of this assumption. We also assume that our environmental model and domain-specific knowledge are correct and do not cause any bugs to be missed. Finally, we assume that the external tools that we use as part of the \whoop toolchain are sound and bug-free.

\medskip\noindent\textbf{Limitations }
%
\whoop is based on lockset analysis and thus can report false bugs, because a violation of the locking discipline does not always correspond to a real data race (e.g.\ when lockfree synchronization is used instead of locking). \whoop also uses over-approximation (e.g.\ when reading from the shared state) and summarization, which can be sources of false positives. Furthermore, the tool does not currently check for dynamically created locks or for locks that are provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently handle interrupt handlers in a special way; to be sound, we assume that they can execute concurrently with entry points at any time. We could address this in the future by modeling interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).
